### 2024-09-19 documentation/supplement.tex
Final edits to text + README

\subsection{Parts and bill-of-materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from aluminium stock in the university machine shop. Aluminium has the added benefit of anodization, which can help control scattered light. An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & MBF Bioscience& 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill-of-materials is provided in the git repository.}\label{tab_costs}
\end{table}

\subsection{Structure and use of this document}
In the following sections, we will cover the setup and alignment of the microscope. This is split into three parts. The first part covers all components on the optical table that serve to condition the beam. The second part focuses on the  95 mm vertical post that holds the scanning mirror and scan lens assemblies. The third part is the microscope head with the attached collection optics. We will begin with the assembly on the optical table. All along, we assume the reader will have downloaded and opened the CAD model as we will rely heavily on it.\newline
Before building your own microscope, read these instructions fully. Check the CAD files, and make sure that the instructions make sense. This document follows closely our own alignment procedure, and we have done our best to be accurate. However, use common sense and do not follow these instructions blindly. Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. Further, prior to the construction, check carefully the instruction manual of the scanning mirrors, photomultiplier tubes (PMTs), power supplies, Pockels cell, ScanImage, the Piezoelectric objective collar, and the filter mounting instructions.

\section{Assembly on the optical table}
%
\subsection{Beam conditioning}
An overview of the system for beam conditioning is shown in Fig.~\ref{sfig1} with key items labelled by capital letters. The following lines will cover the items, and their alignment.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig1.jpg}
    \caption{{\bf Overall view of the beam conditioning path on the optical table.} Shown is a photograph of the components used to condition the beam for our microscope. Key components of the system are labelled with capital letters. The laser is shown as a red transparent line with intensity color coded. The beamsplitter cube (component D) splits the beam into two, halving its power. The Pockels cell (component G) reduces the power further. The reflections out of the Pockels cell and from the shutter (item J) are shown in yellow. The telescope (item K) magnifies the beam $\times 2$. The empty SM1 tube is an anodized aluminum SM1 lens tube cover (SC600, Thorlabs). All parts are explained in the text together with a note on their alignment.}
    \label{sfig1}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} Laser beam coming out of the laser.

@@

    \item \textbf{C)} $\diameter1\text{ in}$ mounted achromatic half-wave plate with SM1-threaded mount (AHWP10M-980, Thorlabs) inside a high-precision rotation mount (PRM1, Thorlabs). First, to check that the beam travels centrally through the half-wave plate, use an iris. Then place the half-wave plate at a slight angle to make sure that the beam reflected of the surface of the half-wave plate does not travel back into the laser. Confirm by using a detector card to find the (weak) back reflection. While doing this, terminate the beam traveling through the half-wave plate with a beam block.

@@

    \item \textbf{G)} Pockels cell (350-80-LA-02 with 302RM driver, Conoptics) sitting on a holder (M102A, Conoptics). Properties of light travelling through this device are controlled electrically through the two connected wires. The alignment of the Pockels cell requires two steps: The Pockels cell has to be aligned with the optical axis of the laser, and be rotated relative to the laser's polarization such that the dynamic range is maximized \cite{Conoptics2018, Scientifica2024}. The first step can be done with an alignment tool of identical geometry to the Pockels cell (Conoptics modulator alignment tool 103). The second step requires the Pockels cell to be connected, and a power measurement performed. Importantly, these steps have to be done under full power because the beam profile in alignment mode might be slightly different from the full beam.
    \begin{itemize}
        \item First, install the holder on the table, and position on it the Conoptics Pockels cell alignment tool (Conoptics modulator alignment tool 103).
        \item Use a power meter on the output side, maximize power going through the central bore by manipulating the 4 bottom screws on the holder.
        \item Then switch the laser to full power and optimize the position of the screws for maximum transmission.
        \item Tighten the screws around the alignment tool, and mark on the screws the optical position. This will be important later to reproduce the exact same position of the alignment tool with the Pockels cell.
        \item Connect the Pockels cell (M350-80LA, Conoptics) to the driver as per the Conoptics instructions (p1m and p2m go to J1m and J2m, p1 and p2 go to the controller). The controller settings are shown in Fig.~\ref{sfig2}.
        %
        \begin{SCfigure}
            \includegraphics[width=.75\textwidth]{sfig2.jpg}
          \caption{{\bf Settings on the Pockels Cell controller.} Shown are the controls of the Pockels Cell driver as set in our system. For reference, see \cite{Conoptics2018}. We recommend for people building a microscope to take many such pictures of all settings and elements.}
          \label{sfig2}
        \end{SCfigure}
        %
        \item Next, determine the best orientation of the Pockels cell, by measuring the controller's voltage for different Pockels cell rotations. For each rotation of the Pockels cell, measure its transmission while turning the dial on the Conoptics controller from one end to the other. Iterate this for different orientations of the Pockels cell until an optimum is found. An example of different transmission curves is shown in the main manuscript, Fig. 9A. The optimal orientation allows to adjust the laser power in the widest range.
        \item The Pockels Cell splits the input beam into a transmitted and a rejected beam. The transmitted beam is used, while the energy of the rejected beam is dissipated in a beam block. By changing the control voltage of the Pockels Cell, the power ratio between the transmitted and rejected beam can be adjusted. The rejected beam leaves the Pockels cell through a bore at its side. During alignment, make sure that the rejected beam is properly terminated with a beam block.
        \item To validate the alignment, compute the extinction ratio of the Pockels cell, i.e. the ratio of maximal and minimal light transmission, and compare that number with the data sheet provided by Conoptics. Ours operate in a regime of $\approx 450$.
        \item Next, set the Pockels cell controller to the control voltage corresponding to minimum light transmission.
        \item Tighten the holder, and confirm that the Pockels cell is still well-aligned.
    \end{itemize}

@@

\item \textbf{M)} Mirror (PF10-03-P0, Thorlabs, inside KCB1) to reflect the beam up at a right angle. For the next steps (in particular finding the optimal scanning mirror position), it is important that the beam travels up perpendicularly to the optical table, and parallel to the 95 mm optical rail column that holds the scanning mirrors (next section).

@@

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}A,B. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labelled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (BPF10-03-P0, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Resonant-Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing (SM2V05, adjustable SM2 Lens Tube, Thorlabs).
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round 2 inch mirror, this could be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This would increase the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

@@

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket (all from the XT95 series, Thorlabs) to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the center of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}) facing up. These two pieces meet in mid-air. The gap in between can be reduced to zero using adjustable length SM1 lens tube (e.g. SM1V10, Thorlabs, not shown in CAD) and can be further closed by a small portion of  lens tube cover (SC600, Thorlabs). 
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}A). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

@@

After the beam's alignment is confirmed by traveling through the two irises, it is time to install, and align scan and tube lens. Remember that (1) the distance between the tube lens (component C in Fig.~\ref{sfig5}) and scan lens (component G in Fig.~\ref{sfig5}) has to be 100 mm + 375 mm = 475 mm while (2) the scanning mirror set (component H in Fig.~\ref{sfig5}) has to be positioned in the focal plane of the scan lens, while (3) the objective back aperture is positioned in the focal plane of the tube lens (see Fig. 1 in the main manuscript). In our design, the objective is fixed. Therefore we have to perform the lens alignment in several steps, conceptually beginning at the back-aperture of the objective.

@@

    \item If the objective requires water immersion, has a drop of water been placed between the sample and the objective.

@@

\begin{itemize}
    \item Place the first element on top of the spanner wrench (Thorlabs SPW604) using lens paper. Check the lens thoroughly. Dust can be blown away with a duster, finger prints wiped off with Methanol and a lens cleaning tissue.
    \item Blow it with the air duster. 
    \item Slide the SM2L10 tube over the element until it sits in the end. Sometimes it needs to be wiggled, but do not force it.
    \item Flip the whole thing over.
    \item Now the element is in the tube. Tighten it with a SM2 retaining ring.
    \item Insert a second SM2 retaining ring for spacing. 
    \item Repeat the previous steps to install the second lens above the SM2 retaining ring
    \item Flip again, blow with air, and set the lens in place with a third SM2 retaining ring. This produces the configuration shown in Fig.~\ref{sfig8}A.
    \item Be careful with dust and fingerprints when putting elements into the tube. Confirm that there are no fingerprints, and no dust particles trapped on or between the lenses.
\end{itemize}
%
Our simulations indicate that the lens spacing between the two doublets is not critical, and the approximate clearance provided by two SM2 spacer rings is sufficient. This is shown in Fig.~\ref{sfig8}A. For more precise placement, a spacer ring like the one shown in Fig.~\ref{sfig8}B can be used. This will be important for the slightly more complex scan lens assembly described in the next section.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig8.jpg}
    \caption{{\bf Assembly of lens groups.} \textbf{A)} Tube lens assembly with the two doublets held in place with spacer rings. \textbf{B)} Assembly method of lenses: Lenses and spacer rings are stacked on a SM2 spanner, ready for the SM2 tubing to be lowered around them. \textbf{C)} Design of the scan lens assembly. Notice the custom spacer rings in blue. The distance between the last element of the scan lens assembly and the scanning mirror box is $\approx 1.35 \text{ inches}$. \textbf{D)} The assembled scan lens group in its SM2 housing.}
    \label{sfig8}
\end{figure}
%
\subsection{Scan lens assembly}
The scan lens assembly is shown in Fig.~\ref{sfig8}C. The individual steps for the scan lens group are as follows:
\begin{itemize}
    \item Place the KPC070AR, a plano-concave lens, on the spanner wrench with the plane side facing out. Check the lens thoroughly for dust and finger prints.
    \item Slide the SM2 tube over the elements until they sit at the end of the tube. Sometimes it needs to be wiggled, to make sure the lenses are seated properly.
    \item Flip the whole thing over.
    \item Tighten it with a SM2 retaining ring.
    \item Next, place the LB1199-B lens on the wrench. This is a bi-convex lens for which the orientation is irrelevant. Flip over the assembly, and tighten the lens with a second SM2 retaining ring. 
    \item For the third and fourth lens, place an ACT508-200-B lens, a spacer ring, the second ACT508-200-B lens, and two spacer rings on the wrench. Make sure you remove all dust from the various surfaces. Flip over the assembly, and tighten the lens with a third SM2 retaining ring. 
    \item Check the assembly for trapped dust or fingerprints. This will produce a lens group like the one shown in Fig.~\ref{sfig8}D.
\end{itemize}

@@

    \item \textbf{F)} Next, we fix the condenser lenses (ACL25416U-A, Thorlabs) in their housing plates. The convex part is facing towards the inside of the box, and set with nylon set screws (Stainless Steel Nylon-Tip Set Screw, 4-40 Thread, 1/8 inch long). The holders are then fixed together with Stainless Steel Socket Head Screw, 8-32 Thread Size, 3/8 inch long.
    \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them. First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8in long). Orientation is important: For this brand of filters, the arrow is following the light path, i.e. away from the inside of the box and towards the PMT.

@@

    \item \textbf{I)} Next, we attach the dichroic mirror that splits red and green light (Semrock Brightline FF562-Di03-40X52, AVR Optics) to its metal holder. The caret points towards the metal holder, such that the side the caret is pointing to contacts the metal when it is glued in place. When the glue has set, the mirror casing is screwed in place using stainless steel socket head screw, 4-40 Thread Size, 5/16 inches long. The glue used is a 5min non-sagging Epoxy. Three dichroic was attached with 3 points of glue of minimal volume.

>>>>

\subsection{Parts and bill of materials}
All custom metal pieces are parts of the CAD assembly of the microscope. Ours were manufactured from aluminium stock in the university machine shop. Aluminium has the added benefit of anodization, which can help control scattered light. An overview of the microscope's cost is shown in Tab.~\ref{tab_costs}. Keep in mind that these prices can significantly change over time, while some products can become unobtainable and need to be replaced with a different or newer model.
%
\begin{table}
\begin{center}
  \begin{tabular}{ l c r } \hline
   \textbf{Item} & \textbf{Info} & \textbf{Cost} \\ \hline
\rowcolor{gray!20} 920 nm fs-pulsed Laser  & Spark Alcor 920 + Warranty & 90 k \\
                   ScanImage DAQ-System \& optimized PC & MBF Bioscience& 20 k \\
\rowcolor{gray!20} Piezo collar & Physik Instrumente & 16 k	\\
            $2\times$ PMTs + preamplifiers  & Hamamatsu \& Thorlabs & 12 k \\
\rowcolor{gray!20} Pockels cell             & Conoptics &	11 k \\
                   Objective                & Nikon &  8 k \\
\rowcolor{gray!20} Machining custom parts   & Machine Shop; as per CAD files &  7 k \\
                   Optical filters          & AVR optics \& Semrock &  7 k \\
\rowcolor{gray!20} Lenses + optomechanics   & Thorlabs \& Newport &  7 k \\
                   Galvo-Resonant Scanner set & Novanta &  6 k \\
\rowcolor{gray!20} Electronics/cables/tools & Newark \& McMaster &  5 k \\
                   Mounting rack            & Emcor Enclosures &  3 k \\
\rowcolor{gray!20} Laser shutter            & Uniblitz/Vincent &  2 k \\
                   Laser safety goggles     & Edmund Optics &  1 k \\
\rowcolor{gray!20} Laser power meter        & Coherent &  1 k \\
                   Agarose \& fluorescent beads     & Thermofisher &  1 k \\
  \hline
 \textbf{Total}                    & & \textbf{197 k} \\
  \hline
  \end{tabular}
\end{center}
\caption{\textbf{Overview of the approximate cost in 2024-US\$} Note that this list excludes the optical table, and any other infrastructure costs such as compressors for air, and associated power supplies. This is just a summary. The detailed bill of materials is provided in the git repository.}\label{tab_costs}
\end{table}

\subsection{Structure and use of this document}
In the following sections, we will cover the setup and alignment of the microscope. This is split into three parts. The first part covers all components on the optical table that serve to condition the beam. The second part focuses on the  95 mm vertical post that holds the scanning mirror and scan lens assemblies. The third part is the microscope head with the attached collection optics. We will begin with the assembly on the optical table. All along, we assume the reader will have downloaded and opened the CAD model as we will rely heavily on it. Further, check carefully the instruction manuals of the scanning mirrors, photomultiplier tubes (PMTs), power supplies, Pockels cell, ScanImage, the Piezoelectric objective collar, and the filter mounting instructions.\newline
Before building your own microscope, read these instructions fully. Check the CAD files, and make sure that the instructions make sense. This document follows closely our own alignment procedure, and we have done our best to be accurate. However, use common sense. Do not follow these instructions blindly (or you will follow these instructions blindly). Like all open instrumentation (under CC-BY-4.0), this work is distributed in the hope that it will be useful, but WITHOUT ANY WARRANTY, to the extent permitted by law; without even the implied warranty of MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.

\section{Assembly on the optical table}
%
\subsection{Beam conditioning}
An overview of the system for beam conditioning is shown in Fig.~\ref{sfig1} with key items labelled by capital letters. The following lines will cover the items, and their alignment.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig1.jpg}
    \caption{{\bf Overall view of the beam conditioning path on the optical table.} Shown is a photograph of the components used to condition the beam for our microscope. Key components of the system are labelled with capital letters. The laser is shown as a red transparent line with intensity color coded. The beamsplitter cube (component D) splits the beam into two, halving its power. The Pockels cell (component G) reduces the power further. The reflections out of the Pockels cell and from the shutter (item J) are shown in yellow. The telescope (item K) magnifies the beam $\times 2$. The empty SM1 tube is an anodized aluminum SM1 lens tube cover (SC600, Thorlabs). All parts are explained in the text together with a note on their alignment.}
    \label{sfig1}
\end{figure}
%
\begin{enumerate}[]
    \item \textbf{A)} Laser head emitting the laser beam (red).

@@

    \item \textbf{C)} $\diameter1\text{ inch}$ mounted achromatic half-wave plate with SM1-threaded mount (AHWP10M-980, Thorlabs) inside a high-precision rotation mount (PRM1, Thorlabs). First, use an iris to check that the beam travels centrally through the half-wave plate. Then place the half-wave plate at a slight angle to make sure that the beam reflected of the surface of the half-wave plate does not travel back into the laser. Confirm by using a detector card to find the (weak) back reflection. While doing this, terminate the beam traveling through the half-wave plate with a beam block.

@@

    \item \textbf{G)} Pockels cell (350-80-LA-02 with 302RM driver, Conoptics) sitting on a holder (M102A, Conoptics). Properties of light travelling through this device are controlled electrically through the two connected wires. The alignment of the Pockels cell requires two steps: The Pockels cell has to be aligned with the optical axis of the laser, and be rotated relative to the laser's polarization such that the dynamic range is maximized \cite{Conoptics2018, Scientifica2024}. The first step can be done with an alignment tool of identical geometry to the Pockels cell (Conoptics modulator alignment tool 103). The second step requires the Pockels cell to be connected, and a power measurement performed. Importantly, these steps have to be done under full power because the beam profile in alignment mode might be slightly different from the full beam.
    \begin{itemize}
        \item First, install the holder on the table, and position on it the Conoptics Pockels cell alignment tool (Conoptics modulator alignment tool 103).
        \item Use a power meter on the output side, maximize power going through the central bore by manipulating the 4 bottom screws on the holder.
        \item Then switch the laser to full power and optimize the position of the screws for maximum transmission.
        \item Tighten the screws around the alignment tool, and mark on the screws the optical position. This will be important later to reproduce the exact same position of the alignment tool with the Pockels cell.
        \item Connect the Pockels cell (M350-80-LA, Conoptics) to the driver as per the Conoptics instructions (p1m and p2m go to J1m and J2m, p1 and p2 go to the controller). The controller settings are shown in Fig.~\ref{sfig2}.
        %
        \begin{SCfigure}
            \includegraphics[width=.75\textwidth]{sfig2.jpg}
          \caption{{\bf Settings on the Pockels Cell controller.} Shown are the controls of the Pockels Cell driver as set in our system. For reference, see \cite{Conoptics2018}. We recommend for people building a microscope to take many such pictures of all settings and elements.}
          \label{sfig2}
        \end{SCfigure}
        %
        \item Next, determine the best orientation of the Pockels cell, by measuring the controller's voltage for different Pockels cell rotations. For each rotation of the Pockels cell, measure its transmission while turning the dial on the Conoptics controller from one end to the other. Iterate this for different orientations of the Pockels cell until an optimum is found. An example of different transmission curves is shown in the main manuscript, Fig. 9A. The optimal orientation allows to adjust the laser power in the widest range.
        \item The Pockels Cell splits the input beam into a transmitted and a rejected beam. The transmitted beam is used, while the energy of the rejected beam is dissipated in a beam block. By changing the control voltage of the Pockels Cell, the power ratio between the transmitted and rejected beam can be adjusted. The rejected beam leaves the Pockels cell through a bore at its side. During alignment, make sure that the rejected beam is properly terminated with a beam block.
        \item To validate the alignment, compute the extinction ratio of the Pockels cell, i.e. the ratio of maximal and minimal light transmission, and compare that number with the data sheet provided by Conoptics. Ours operate in a regime of $\approx 450$.
        \item Next, set the Pockels cell controller to the control voltage corresponding to minimum light transmission.
        \item Tighten the holder, and confirm that the Pockels cell is still well-aligned.
    \end{itemize}

@@

\item \textbf{M)} Mirror (PF10-03-P01, Thorlabs, inside KCB1) to reflect the beam up at a right angle. For the next steps (in particular finding the optimal scanning mirror position), it is important that the beam travels up perpendicularly to the optical table, and parallel to the 95 mm optical rail column that holds the scanning mirrors (next section).

@@

Following beam conditioning on the optical table, the beam is reflected up from the optical table towards the ceiling into a box housing the scanning mirrors. This is shown in Fig.~\ref{sfig4}A,B. Following the scanning mirrors, the beam travels up through the scan lens, and directed to the microscope head with another mirror.
%
\begin{figure}[h]
    \includegraphics[width=\textwidth]{sfig4.jpg}
    \caption{{\bf Overall view of the scanning post.} \textbf{A)} Side few. Key components of the system are labelled with capital letters. These are explained in the text together with a note on how to align these components. Importantly, the machined block (C) houses the scanning mirrors, and the scan lens assembly is placed in the SM2 house labelled (E). \textbf{B)} Frontal view. The PMT preamplifiers (component G) and the scanning mirror power supply (component H) are visible.}
    \label{sfig4}
\end{figure}
%
%
\begin{enumerate}[]
    \item \textbf{A)} Mirror (PF10-03-P01, inside KCB1, with CP12 attached) - turn the beam at a right angle.
    \item \textbf{B)} Broadband filter (WG11010-B, Thorlabs, inside SM1L20 and SM1S20) - filter to keep dust out of the box housing the scanning mirrors.
    \item \textbf{C)} An aluminium box containing the resonant and slow galvanometer set (CRS8K/6215H Resonant-Galvo Set, Novanta), mounted to 95 mm rail (XT95RC4, Thorlabs). A detailed description is provided below.
    \item \textbf{D)} Empty tubing (SM2V05, adjustable SM2 Lens Tube, Thorlabs).
    \item \textbf{E)} Scan lens - See detailed description below.
    \item \textbf{F)} Mirror in its housing (PF20-03-P01 and KCB2, both Thorlabs). While we used a round 2 inch mirror, this should be replaced with an elliptical mirror and housing (PFE20-P01 and KCB2EC, both Thorlabs). This would increase the field-of-view because the cross-section of an ellipse at 45 degrees is a circle. At low magnification, a round mirror will lead to vignetting.
    \item \textbf{G)} PMT preamplifier (TIA60, Thorlabs) attached to a 95 mm rail.
    \item \textbf{H)} Power supply for the scanning mirrors (part of the Novanta scanning mirror set) housed in an electronics prototype box.
\end{enumerate}

@@

\begin{itemize}
    \item First, mount the 95 mm rail to the table. Then attach a bracket (all from the XT95 series, Thorlabs) to the side to hold the scan lens (component D in Fig.~\ref{sfig3}), and one on top with a cage system to hold a mirror (component F in Fig.~\ref{sfig3}). For alignment with cage systems, we use a cage system alignment plate (VRC4CPT, Thorlabs). The rest of the assembly here will be done without any lenses. The goal is a well-aligned beam that travels through the center of all parts, and parallel to the optomechanical surfaces.
    \item The box housing the scanning mirrors is connected, trough SM1 tubing, to a mirror (component A in Fig.~\ref{sfig3}). To align this upper periscope mirror with the lower periscope mirror, mounted on the table, connect a piece of SM1 tubing to the upper mirror facing down, and  a second piece of SM1 tubing to the table mirror facing up (component M in Fig.~\ref{sfig1}). These two pieces meet in mid-air. The gap in between can be reduced to zero using adjustable length SM1 lens tube (e.g. SM1V10, Thorlabs, not shown in CAD) and can be further closed by a small portion of  lens tube cover (SC600, Thorlabs). 
    \item Next, we adjust the mirror (component A in Fig.~\ref{sfig4}A) so that light travels through the center of the scanning mirrors and up the 95 mm rail. This is done with irises. One is attached at the entry port of the scanning mirror box, e.g. in the SM1 tube (component B in Fig.~\ref{sfig4}A). Another two irises are attached, as far away as possible, to a 95 mm rail bracket. It is convenient to use the future holder of the scan lens (component D/E in Fig.~\ref{sfig4}). This ensures that the beam will pass through the center of the scan lens. As the mirror (component F in Fig.~\ref{sfig4}) is not installed yet, an IR detection card can conveniently be taped to the ceiling to make sure that the beam is on-axis. Of note, the resonant scanner is at its origin point when no power is being provided, but the slow galvanometer needs to be provided 0 Volt to position the mirror at its origin point. This can be done through the voltage supply, or to a good approximation through ScanImage by setting the scan mode to the highest possible zoom level. In our microscope design, it can be helpful to wiggle the lid to which the scanning mirrors are mounted (item C in Fig.~\ref{sfig4}). This step is tricky and can require some patience. 
    \item When confirmed that the light travels parallel to the 95 mm rail, we attach the mirror (component F in Fig.~\ref{sfig4}), and slide it along the cage rods to a position where the beam is reflected centrally through the caging system and the mount positioned on top of the 95 mm rail. This is done using the same set of two SM2-mounted irises that we used to make sure that light leaves the scanning mirror box without x or y displacement. The beam is now ready to travel through the microscope head.
\end{itemize}

@@

After the beam's alignment is confirmed by traveling through the two irises, it is time to install, and align scan and tube lens. Remember that (1) the distance between the tube lens (component C in Fig.~\ref{sfig5}) and scan lens (component G in Fig.~\ref{sfig5}) has to be 100 mm + 375 mm = 475 mm while (2) the scanning mirror set (component H in Fig.~\ref{sfig5}) has to be positioned in the focal plane of the scan lens (see Fig. 1 in the main manuscript). In our design, the objective is fixed. Therefore we have to perform the lens alignment in several steps, conceptually beginning at the back-aperture of the objective.

@@

    \item If the objective requires water immersion, has a drop of water been placed between the sample and the objective?

@@

\begin{itemize}
    \item Place the first element on top of the spanner wrench (Thorlabs SPW604) using lens paper. Check the lens thoroughly. Dust can be blown away with a duster, finger prints wiped off with Methanol and a lens cleaning tissue.
    \item Blow it with the air duster. 
    \item Slide the SM2L10 tube over the element until it sits in the end. Sometimes it needs to be wiggled, but do not force it.
    \item Flip the whole thing over.
    \item Now the element is in the tube. Tighten it with a SM2 retaining ring.
    \item Insert a second SM2 retaining ring for spacing. 
    \item Repeat the previous steps to install the second lens above the SM2 retaining ring
    \item Flip again, blow with air, and set the lens in place with a third SM2 retaining ring. This produces the configuration shown in Fig.~\ref{sfig8}A.
    \item Be careful with dust and fingerprints when putting elements into the tube. Confirm that there are no fingerprints, and no dust particles trapped on or between the lenses.
\end{itemize}
%
Our simulations indicate that the lens spacing between the two doublets is not critical, and the approximate clearance provided by two SM2 spacer rings is sufficient. This is shown in Fig.~\ref{sfig8}A. For more precise placement, a spacer ring like the one shown in Fig.~\ref{sfig8}B can be used. This will be important for the slightly more complex scan lens assembly described in the next section.
%
\begin{figure}[!t]
    \includegraphics[width=\textwidth]{sfig8.jpg}
    \caption{{\bf Assembly of lens groups.} \textbf{A)} Tube lens assembly with the two doublets held in place with spacer rings. \textbf{B)} Assembly method of lenses: Lenses and spacer rings are stacked on a SM2 spanner, ready for the SM2 tubing to be lowered around them. \textbf{C)} Design of the scan lens assembly. Notice the custom spacer rings in blue. The distance between the last element of the scan lens assembly and the scanning mirror box is $\approx 1.35 \text{ inch}$. \textbf{D)} The assembled scan lens group in its SM2 housing.}
    \label{sfig8}
\end{figure}
%
\subsection{Scan lens assembly}
The scan lens assembly is shown in Fig.~\ref{sfig8}C. The individual steps for the scan lens group are as follows:
\begin{itemize}
    \item Place the KPC070AR, a plano-concave lens, on the spanner wrench with the plane side facing out. Check the lens thoroughly for dust and finger prints.
    \item Slide the SM2 tube over the elements until they sit at the end of the tube. Sometimes it needs to be wiggled, to make sure the lenses are seated properly.
    \item Flip the whole thing over.
    \item Tighten it with a SM2 retaining ring.
    \item Next, place the LB1199-B lens on the wrench. This is a bi-convex lens for which the orientation is irrelevant. Flip over the assembly, and tighten the lens with a second SM2 retaining ring. 
    \item For the third and fourth lens, place an ACT508-200-B lens, a spacer ring, the second ACT508-200-B lens, and two spacer rings on the wrench. Make sure you remove all dust from the various surfaces. Flip over the assembly, and tighten the lens with a third SM2 retaining ring. 
    \item Check the assembly for trapped dust or fingerprints. This will produce a lens group like the one shown in Fig.~\ref{sfig8}D.
\end{itemize}

@@

    \item \textbf{F)} Next, we fix the condenser lenses (ACL25416U-A, Thorlabs) in their housing plates. The convex part is facing towards the inside of the box, and set with nylon set screws (Stainless Steel Nylon-Tip Set Screw, 4-40 Thread, 1/8 inch long). The holders are then fixed together with stainless steel socket head screw, 8-32 thread size, 3/8 inch long.
    \item \textbf{G)} With the condensers in place, we can install the optical band-pass filters in front of them. First the 525 nm band-pass filter (Semrock Brightline FF01-525/45-32, AVR Optics) for the green channel, which is secured with a nylon set screw (stainless steel nylon-tip set screw, 4-40 thread, 1/8 inch long). Orientation is important: For this brand of filters, the arrow is following the light path, i.e. away from the inside of the box and towards the PMT.

@@

    \item \textbf{I)} Next, we attach the dichroic mirror that splits red and green light (Semrock Brightline FF562-Di03-40X52, AVR Optics) to its metal holder. The caret points towards the metal holder, such that the side the caret is pointing to contacts the metal when it is glued in place. When the glue has set, the mirror casing is screwed in place using stainless steel socket head screw, 4-40 thread size, 5/16 inch long. The glue used is a 5 min non-sagging Epoxy. Three dichroic was attached with 3 points of glue of minimal volume.
